Consistent Polyhedral Surrogates via Embedding

### 2019-05-20 notes/jessie-proof-sketches.tex
Added matching losses condition on prop 1 proof

  \jessie{Redone.  Original version in comments below.}
  For the forward implication, suppose $L$ embeds the discrete loss $\ell$ via the embedding $\varphi$.
  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma:\simplex \toto \R$ elicited by $\ell$.
  Call $\R' := \varphi(\R)$.
  For all $p \in \simplex$, we know that $\Gamma(p) = \varphi(\gamma(p))$ \raf{Not true; focus on the next statement and show directly using def of embedding}.
  We know $\gamma' := \Gamma(p) \cap \R'$ is nonempty for all $p \in \simplex$ since $\Gamma(p) = \varphi(\gamma(p)) \subseteq \R'$.
  By \jessie{COLT Lemma 11}, we know that $L|_{\R'}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\R'}}$.

@@

  To start, assume that $\risk{L} = \risk{\ell}$.
  The projection of the epigraphs onto $\simplex$ must then form the same power diagram \jessie{COLT Theorem 33}, corresponding to the level sets of the properties each loss elicits.
  Notably, \jessie{as in proof of COLT Prop 12,} the facets of $\risk{\ell}$ project onto the level sets of $\gamma := \prop{\ell}$.
  As $\ell$ is discrete, we know $\gamma$ is finite \raf{note for later: we have to be careful about ``discrete'' and ``finite'' since they both bake in regularity conditions, like nondegeneracy as you mention, but also non-redundancy}, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
  Since the risks of $L$ and $\ell$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, \raf{wait, you skipped the other condition for losses embedding each other $\rightarrow$} and thus $L$ embeds the discrete loss $\ell$.

>>>>

  \jessie{Redone.  Original version in comments below.}
  For the forward implication, suppose $L$ embeds the discrete loss $\ell$ via the embedding $\varphi$.
  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma:\simplex \toto \R$ elicited by $\ell$.
  Call $\R' := \varphi(\R)$.
  %For all $p \in \simplex$, we know that $\varphi(\gamma(p)) \subseteq \Gamma(p)$ \raf{Not true; focus on the next statement and show directly using def of embedding}.
  We know $\gamma' := \Gamma(p) \cap \R'$ is nonempty for all $p \in \simplex$ since $\varphi(\gamma(p)) \subseteq \R' \subseteq \Gamma(p)$.
  By \jessie{COLT Lemma 11}, we know that $L|_{\R'}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\R'}}$.

@@

  To start, assume that $\risk{L} = \risk{\ell}$.
  The projection of the epigraphs onto $\simplex$ must then form the same power diagram \jessie{COLT Theorem 33}, corresponding to the level sets of the properties each loss elicits.
  Notably, \jessie{as in proof of COLT Prop 12,} the facets of $\risk{\ell}$ project onto the level sets of $\gamma := \prop{\ell}$.
  As $\ell$ is discrete, we know $\gamma$ is finite \raf{note for later: we have to be careful about ``discrete'' and ``finite'' since they both bake in regularity conditions, like nondegeneracy as you mention, but also non-redundancy}, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
  Since the risks of $L$ and $\ell$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, \raf{wait, you skipped the other condition for losses embedding each other $\rightarrow$} and thus $L$ embeds the discrete loss $\ell$ if $\ell(r) = L(\varphi(r))$ for all $r \in \R$.

  To see this, assume that for some $r \in \R$ that $\ell(r) \neq L(\varphi(r))$.
  Then for any distribution $p$ such that $p \in \gamma_r$, we know that $r \in \argmin_{r'} \ell(r', p)$.
  If $\ell(r, p) < L(\varphi(r), p)$, then we contradict the embedding result of the properties, as $r \in \gamma(p)$, but $\varphi(r) \not\in \Gamma(p)$, as there is some other report that yields a strictly lower loss for $L$.
  Similarly, for any $p' \in \Gamma_{\varphi(r)}$, we know that $\varphi(r) \in \argmin_u L(u, p')$.
  If $\ell(r, p') > L(\varphi(r), p')$, then we again contradict the property embedding, as $\varphi(r) \in \Gamma(p')$, but $r \not\in \gamma(p')$.
  However, there is some other report that yields a lower loss for $\ell$, given that the risks are the same.
  Therefore, we must have $\ell(r) = L(\varphi(r))$ for all $r \in \R$, and conclude that $L$ embeds the discrete loss $\ell$.
